---
title: "Final Project"
author: "Matthew Kirby"
date: "2/22/2015"
output: html_document
---

Begin by loading the data file.
```{r}
setwd("~/git_demo_iplant")
fulldata.in <- read.delim("output/combined_gapMinder.tsv", sep="\t")
```

Now separate the data for Syria, Peru and Poland.
```{r}
Syria.in <- subset(fulldata.in, country == "Syria")
Peru.in <- subset(fulldata.in, country == "Peru")
Poland.in <- subset(fulldata.in, country == "Poland")
```

Now I want to make a scatter plot of GDP per capita per year for these three countries
```{r}
library("ggplot2")
ggplot(Peru.in, aes(year, gdpPercap)) + geom_point() + ggtitle("Peru")
ggplot(Poland.in, aes(year, gdpPercap)) + geom_point() + ggtitle("Poland")
ggplot(Syria.in, aes(year, gdpPercap)) + geom_point() + ggtitle("Syria")
```
I notice that the three curves trend upwards. All three contries experience a spike downward around 1990.

Next I want to calculate the mean life expectancies for each continent.
```{r}
aggregate(fulldata.in$lifeExp, list(fulldata.in$continent), mean)
```

The max life expenetancy
```{r}
aggregate(fulldata.in$lifeExp, list(fulldata.in$continent), max)
```

And the min life expectancy
```{r}
aggregate(fulldata.in$lifeExp, list(fulldata.in$continent), min)
```


Finally I want to make two histograms of global life expectancies

```{r}
ggplot(fulldata.in, aes(



```














